---
title: "ETL"
output: html_document
---

# ETL process to get Corruption Perception Index by sources and year

##Download datasets from website and import
Datasets are downloaded from Transparency International's website.
There is one Excel file per year. 

```{r,warning=FALSE,message=FALSE}
library(readxl)
library(dplyr)
library(ggplot2)
library(reshape)
library(here)

# Data import
cpi_2012 <- read_excel(here("data","CPI2012_Results.xlsx"), sheet = "CPI 2012")
cpi_2013 <- read_excel(here("data","CPI2013_Results.xlsx"), sheet = "CPI 2013")
cpi_2014 <- read_excel(here("data","CPI 2014_FullDataSet.xlsx"), sheet = "CPI 2014")
cpi_2015 <- read_excel(here("data","CPI_2015_FullDataSet.xlsx"), sheet = "CPI 2015")
cpi_2016 <- read_excel(here("data","CPI2016.xlsx"), sheet = "CPI_2016")
cpi_2017_america <- read_excel(here("data","CPI2017_Full_DataSet_.xlsx"), sheet = "Americas", skip = 2)
cpi_2017_asia_pacific <- read_excel(here("data","CPI2017_Full_DataSet_.xlsx"), sheet = "Asia & the Pacific", skip = 2)
cpi_2017_eastern_europe <- read_excel(here("data","CPI2017_Full_DataSet_.xlsx"), sheet = "Eastern Europe & Central Asia", skip = 2)
cpi_2017_western_europe <- read_excel(here("data","CPI2017_Full_DataSet_.xlsx"), sheet = "Western Europe", skip = 2)
cpi_2017_MENA <- read_excel(here("data","CPI2017_Full_DataSet_.xlsx"), sheet = "MENA", skip = 2)
cpi_2017_SubS_Africa <- read_excel(here("data","CPI2017_Full_DataSet_.xlsx"), sheet = "Sub-Saharan Africa", skip = 2)
cpi_2017_african_union <- read_excel(here("data","CPI2017_Full_DataSet_.xlsx"), sheet = "African Union", skip = 2)
cpi_2017_arab_states <- read_excel(here("data","CPI2017_Full_DataSet_.xlsx"), sheet = "Arab States", skip = 2)
cpi_2018 <- read_excel(here("data","2018_CPI_FullDataSet.xlsx"), sheet = "CPI2018", skip = 2)
```
### Table with country and Region
```{r}
country_region <- cpi_2018[c('Country','Region')]
```


## 2017 dataset unification
Data for 2017 is separated by region in different sheets. All the sheets were downloaded separetly.
All the data is unified so that it only one dataset for 2017.

```{r}
# Find differences in column names
dif <- setdiff(names(cpi_2017_african_union),names(cpi_2017_arab_states))

# Rename columns in Arab States dataset to match the rest of datasets
names(cpi_2017_arab_states)[3]<-"CPI Score 2017"
names(cpi_2017_arab_states)[4]<-"Rank 2017"
names(cpi_2017_arab_states)[5]<-"Standard error 2017"
names(cpi_2017_arab_states)[8]<-"Sources"

# list all dataframes of 2017
list_df <- mget(ls(pattern = "2017"))

# append 2017 dataframes
cpi_2017 <- do.call("rbind", list_df)

# remove nulls
cpi_2017 <- cpi_2017[rowSums(is.na(cpi_2017)) != ncol(cpi_2017),]

# remove duplicates
cpi_2017<- cpi_2017[!duplicated(cpi_2017$Country), ]

# delete all datasets of 2017 by region
rm(cpi_2017_african_union,cpi_2017_america,cpi_2017_arab_states,cpi_2017_asia_pacific,cpi_2017_eastern_europe,cpi_2017_SubS_Africa,cpi_2017_MENA,cpi_2017_western_europe)
```


## Add column with year
Add a column to identify the year

```{r}
cpi_2012 <- cpi_2012 %>% rowwise() %>% mutate(year = 2012)
cpi_2012 <- cpi_2012 %>%select(year, everything())
cpi_2013 <- cpi_2013 %>% rowwise() %>% mutate(year = 2013)
cpi_2013 <- cpi_2013 %>%select(year, everything())
cpi_2014 <- cpi_2014 %>% rowwise() %>% mutate(year = 2014)
cpi_2014 <- cpi_2014 %>%select(year, everything())
cpi_2015 <- cpi_2015 %>% rowwise() %>% mutate(year = 2015)
cpi_2015 <- cpi_2015 %>%select(year, everything())
cpi_2016 <- cpi_2016 %>% rowwise() %>% mutate(year = 2016)
cpi_2016 <- cpi_2016 %>%select(year, everything())
cpi_2017 <- cpi_2017 %>% rowwise() %>% mutate(year = 2017)
cpi_2017 <- cpi_2017 %>%select(year, everything())
cpi_2018 <- cpi_2018 %>% rowwise() %>% mutate(year = 2018)
cpi_2018 <- cpi_2018 %>%select(year, everything())
```

# Normalize column names
The names of the sources change from year to year, for example in 2012 '' is named as 'BF(SGI)'. 
Before appending all dataframes it is necesary to normalize columnames. The names from 2018 will be taken as correct name.  

```{r}
# 2018 
names(cpi_2018)[5] <-'CPI Score'

cpi_2018['Standard error'] <- NULL
cpi_2018['Region'] <- NULL
cpi_2018['ISO3'] <- NULL
cpi_2018['Rank'] <- NULL
cpi_2018['Number of sources'] <- NULL
cpi_2018['Upper CI'] <- NULL
cpi_2018['Lower CI'] <- NULL

# 2017 
names(cpi_2017)[4]<-"CPI Score"

cpi_2017['ISO3'] <- NULL
cpi_2017['Standard error 2017'] <- NULL
cpi_2017['Rank 2017'] <- NULL
cpi_2017['Sources'] <- NULL
cpi_2017['Upper CI 2017'] <- NULL
cpi_2017['Lower CI 2017'] <- NULL

# 2016 
names(cpi_2016)[3]<-"CPI Score"

cpi_2016['Rank'] <- NULL
cpi_2016['...19'] <- NULL
cpi_2016['Region'] <- NULL
cpi_2016['WB Code'] <- NULL

colnames(cpi_2016)[which(names(cpi_2016) == "Varities of Democracy Project")] <- "Varieties of Democracy Project"

#2015
names(cpi_2015)[6]<-"CPI Score"
names(cpi_2015)[3]<-"Country"

cpi_2015['Country Rank'] <- NULL
cpi_2015['Country Code'] <- NULL
cpi_2015['Region'] <- NULL
cpi_2015['Std Error'] <- NULL
cpi_2015['Number of Surveys Used'] <- NULL
cpi_2015['Min'] <- NULL
cpi_2015['Max'] <- NULL
cpi_2015['90% Lower CI'] <- NULL
cpi_2015['90%Upper CI'] <- NULL

colnames(cpi_2015)[which(names(cpi_2015) == "Arican Development Bank")] <- "African Development Bank CPIA"
colnames(cpi_2015)[which(names(cpi_2015) == "Bertelsmann  Foundation TI")] <- "Bertelsmann Foundation Transformation Index"
colnames(cpi_2015)[which(names(cpi_2015) == "Freedom House NIT")] <- "Freedom House Nations in Transit Ratings"
colnames(cpi_2015)[which(names(cpi_2015) == "IMD World Competitiveness Yearbook")] <- "IMD World Competitiveness Year Book"
colnames(cpi_2015)[which(names(cpi_2015) == "World  Economic Forum EOS")] <- "World Economic Forum EOS"
colnames(cpi_2015)[which(names(cpi_2015) == "Bertelsmann Foundation SGI")] <- "Bertelsmann Foundation Sustainable Governance Index"
colnames(cpi_2015)[which(names(cpi_2015) == "Economist Intelligence Unit")] <- "Economist Intelligence Unit Country Ratings"
colnames(cpi_2015)[which(names(cpi_2015) == "IHS Global Insight")] <- "Global Insight Country Risk Ratings"
colnames(cpi_2015)[which(names(cpi_2015) == "PRS Internationl Country Risk Guide")] <- "PRS International Country Risk Guide"
colnames(cpi_2015)[which(names(cpi_2015) == "World Justice Project ROL")] <- "World Justice Project Rule of Law Index"
colnames(cpi_2015)[which(names(cpi_2015) == "IMD World Competitiveness Year Book")] <- "IMD World Competitiveness Yearbook"

#2014
names(cpi_2014)[6]<-"CPI Score"
names(cpi_2014)[3]<-"Country"

cpi_2014['Country Rank'] <- NULL
cpi_2014['Country Code'] <- NULL
cpi_2014['Std Error'] <- NULL
cpi_2014['Region'] <- NULL
cpi_2014['Number of Surveys Used'] <- NULL
cpi_2014['Min'] <- NULL
cpi_2014['Max'] <- NULL
cpi_2014['90% Lower CI'] <- NULL
cpi_2014['90% Upper CI'] <- NULL

colnames(cpi_2014)[which(names(cpi_2014) == "AFDB")] <- "African Development Bank CPIA"
colnames(cpi_2014)[which(names(cpi_2014) == "BF (BTI)")] <- "Bertelsmann Foundation Transformation Index"
colnames(cpi_2014)[which(names(cpi_2014) == "FH")] <- "Freedom House Nations in Transit Ratings"
colnames(cpi_2014)[which(names(cpi_2014) == "IMD")] <- "IMD World Competitiveness Yearbook"
colnames(cpi_2014)[which(names(cpi_2014) == "WEF")] <- "World Economic Forum EOS"
colnames(cpi_2014)[which(names(cpi_2014) == "BF (SGI)")] <- "Bertelsmann Foundation Sustainable Governance Index"
colnames(cpi_2014)[which(names(cpi_2014) == "EIU")] <- "Economist Intelligence Unit Country Ratings"
colnames(cpi_2014)[which(names(cpi_2014) == "GI")] <- "Global Insight Country Risk Ratings"
colnames(cpi_2014)[which(names(cpi_2014) == "WJP")] <- "World Justice Project Rule of Law Index"

colnames(cpi_2014)[which(names(cpi_2014) == "WB")] <- "World Bank CPIA"
colnames(cpi_2014)[which(names(cpi_2014) == "ICRG")] <- "PRS International Country Risk Guide"
colnames(cpi_2014)[which(names(cpi_2014) == "PERC")] <- "PERC Asia Risk Guide"


#2013
names(cpi_2013)[8]<-"CPI Score"
names(cpi_2013)[3]<-"Country"

cpi_2013['Country Rank'] <- NULL
cpi_2013['Standard Error'] <- NULL
cpi_2013['Country Rank...1'] <- NULL
cpi_2013['Country Rank...6'] <- NULL
cpi_2013['Country Code'] <- NULL
cpi_2013['WB Code'] <- NULL
cpi_2013['IFS Code'] <- NULL
cpi_2013['Region'] <- NULL
cpi_2013['Country Rank'] <- NULL
cpi_2013['Surveys Used'] <- NULL
cpi_2013['MIN'] <- NULL
cpi_2013['MAX'] <- NULL
cpi_2013['Lower'] <- NULL
cpi_2013['Upper'] <- NULL

colnames(cpi_2013)[which(names(cpi_2013) == "AFDB")] <- "African Development Bank CPIA"
colnames(cpi_2013)[which(names(cpi_2013) == "BF (BTI)")] <- "Bertelsmann Foundation Transformation Index"
colnames(cpi_2013)[which(names(cpi_2013) == "FH")] <- "Freedom House Nations in Transit Ratings"
colnames(cpi_2013)[which(names(cpi_2013) == "IMD")] <- "IMD World Competitiveness Yearbook"
colnames(cpi_2013)[which(names(cpi_2013) == "WEF")] <- "World Economic Forum EOS"
colnames(cpi_2013)[which(names(cpi_2013) == "BF (SGI)")] <- "Bertelsmann Foundation Sustainable Governance Index"
colnames(cpi_2013)[which(names(cpi_2013) == "EIU")] <- "Economist Intelligence Unit Country Ratings"
colnames(cpi_2013)[which(names(cpi_2013) == "GI")] <- "Global Insight Country Risk Ratings"
colnames(cpi_2013)[which(names(cpi_2013) == "WJP")] <- "World Justice Project Rule of Law Index"

colnames(cpi_2013)[which(names(cpi_2013) == "WB")] <- "World Bank CPIA"
colnames(cpi_2013)[which(names(cpi_2013) == "ICRG")] <- "PRS International Country Risk Guide"
colnames(cpi_2013)[which(names(cpi_2013) == "PERC")] <- "PERC Asia Risk Guide"

#2012
names(cpi_2012)[5]<-"CPI Score"
names(cpi_2012)[3]<-"Country"

cpi_2012['WB Code'] <- NULL
cpi_2012['Region'] <- NULL
cpi_2012['Country Rank'] <- NULL
cpi_2012['Standard Error'] <- NULL
cpi_2012['...3'] <- NULL
cpi_2012['Surveys Used'] <- NULL
cpi_2012['MIN'] <- NULL
cpi_2012['MAX'] <- NULL
cpi_2012['Lower'] <- NULL
cpi_2012['Upper'] <- NULL

colnames(cpi_2012)[which(names(cpi_2012) == "AFDB")] <- "African Development Bank CPIA"
colnames(cpi_2012)[which(names(cpi_2012) == "BF (BTI)")] <- "Bertelsmann Foundation Transformation Index"
colnames(cpi_2012)[which(names(cpi_2012) == "FH")] <- "Freedom House Nations in Transit Ratings"
colnames(cpi_2012)[which(names(cpi_2012) == "IMD")] <- "IMD World Competitiveness Yearbook"
colnames(cpi_2012)[which(names(cpi_2012) == "WEF")] <- "World Economic Forum EOS"
colnames(cpi_2012)[which(names(cpi_2012) == "BF (SGI)")] <- "Bertelsmann Foundation Sustainable Governance Index"
colnames(cpi_2012)[which(names(cpi_2012) == "EIU")] <- "Economist Intelligence Unit Country Ratings"
colnames(cpi_2012)[which(names(cpi_2012) == "GI")] <- "Global Insight Country Risk Ratings"
colnames(cpi_2012)[which(names(cpi_2012) == "WJP")] <- "World Justice Project Rule of Law Index"

colnames(cpi_2012)[which(names(cpi_2012) == "WB")] <- "World Bank CPIA"
colnames(cpi_2012)[which(names(cpi_2012) == "ICRG")] <- "PRS International Country Risk Guide"
colnames(cpi_2012)[which(names(cpi_2012) == "PERC")] <- "PERC Asia Risk Guide"

```

# Create one dataset with all the data

```{r}
# list sources and dataset
sources = names(cpi_2018)
sources <- sources[!sources %in% c('year','Country')]
list_datasets = list('2018' = cpi_2018,
                     '2017' = cpi_2017,
                     '2016' = cpi_2016,
                     '2015' = cpi_2015,
                     '2014' = cpi_2014,
                     '2013' = cpi_2013,
                     '2012' = cpi_2012)
# Empty dataframe
table = data.frame()

# Melt and append all the data in the one dataframe
for (dataset in list_datasets){
  if (dataset$year[1] %in% c(2015,2014,2013,2012))
    {newsources <- sources[!sources %in% c('Varieties of Democracy Project')]}
  else
    {newsources <- sources}
  for(source in newsources){
      df <- melt(dataset[c('year','Country',source)], id=(c("year","Country")))
      table <- rbind(table,df)
      }
}

# Add region
dataset<- merge(table,country_region, by  = "Country") 

# Change column names
names(dataset)[3] <- 'Source'
names(dataset)[4] <- 'Cpi'

# Save dataset in new csv file
write.csv(dataset, here('data','cpi_across_years.csv'), row.names = FALSE)
```











